### 2019-12-16 thesis/txt/5-study.tex
incorporate prof. knapps feedback on formulas

\paragraph{RQ2.3: Accuracy Metrics}
To measure the accuracy of the retrieved chunks we save the output lines of the chunk retrieval run on the input of the test example ($retrievedlines$).
As oracle in our evaluation, we save the desired lines from the output of the test example ($desiredlines$).

We calculate the following metrics:
\begin{itemize}
	 \itemsep0.5em
	\item True positives: $TP = desiredlines \cap retrievedlines$
	\item Precision: $Precision =  \frac{\# TP}{\# retrievedlines}$
	\item Recall: $Recall = \frac{\# TP}{\# desiredlines}$
	\item F$_{1}$-score: $2 * \frac{Precision * Recall}{Precision + Recall}$
	\item Successful retrieval: $true\ if\ Recall = 1$
\end{itemize}

Precision of a chunk retrieval describes which proportion of the retrieved lines were targeted.
Recall of a chunk retrieval describes which proportion of the targeted lines were retrieved.
Throughout the presentation and discussion of our results we show these two metrics separate, as they might have a different weight when choosing a suitable technique for a task.
In addition, we calculate the F1-Score, the harmonic mean of precision and recall.
We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.

>>>>

\paragraph{RQ2.3: Accuracy Metrics}
To measure the accuracy of the retrieved chunks we save the output lines of the chunk retrieval run on the input of the test example ($\mathit{RetrievedLines}$).
As oracle in our evaluation, we save the desired lines from the output of the test example ($\mathit{DesiredLines}$).

We calculate the following metrics:
\begin{itemize}
	 \itemsep0.75em
	\item True positives: $\mathit{DesiredLines} \cap \mathit{RetrievedLines}$
	\item Precision: $\dfrac{\# \mathit{TruePositives}}{\# \mathit{RetrievedLines}}$
	\item Recall: $\dfrac{\# \mathit{TruePositives}}{\# \mathit{DesiredLines}}$
	\item F$_{1}$-score: $2 \cdot \dfrac{\mathit{Precision} \cdot \mathit{Recall}}{\mathit{Precision} + \mathit{Recall}}$
	\item Successful retrieval: $\mathit{true}\ \mathit{if}\ \mathit{Recall} = 1$
\end{itemize}

Precision of a chunk retrieval describes which proportion of the retrieved lines were targeted.
Recall of a chunk retrieval describes which proportion of the targeted lines were retrieved.
Throughout the presentation and discussion of our results we show these two metrics separate, as they might have a different weight when choosing a suitable technique for a task.
In addition, we calculate the F1-score, the harmonic mean of precision and recall.
We define a successful retrieval as one where all desired lines were extracted, therefore when recall is one.
